**Density Dependence**

### 2023-02-13 Rmd/report mac.Rmd
Report.R & report MAC.rmd

<!-- ## Mackerel report -->

@@

@@

This report deals with the evaluation of density dependent processes for `r mystkname` using Management Strategy Evaluation (MSE). Four alternatives MSE's have been included:

@@

All MSE's have been developed within the FLR framework [ref] and all the code is stored on github [ref].

All data and results are available on DropBox [ref]

# On density-dependent processes

@@

@@

# OM conditioning

@@

```{r, mac.data2, echo=FALSE, fig.asp=1.0, fig.align="center", message=FALSE, warning=FALSE, cache=FALSE}

# sr=fmle(as.FLSR(om,model="bevholt"),control=list(silent=TRUE))
# eq=FLBRP(om,sr=sr)
# 
# om=fwdWindow(om,end=maxyear,eq)
# f =fbar(om)[,ac(2021:maxyear)]%=%refpts(eq)["msy","harvest"]
# om=fwd(om,fbar=f,sr=eq)
# 
# om2=om
# om3=om
# om4=om
# 
# for (iYear in ac(2021:maxyear)){
#   om2=ddFn(iYear,om2,par)
#   om2=fwd(om2,fbar=f[,iYear]*0.8,sr=eq)
# 
#   om3=ddFn(iYear,om3,par)
#   om3=fwd(om3,fbar=f[,iYear],sr=eq)
#   
#   om4=ddFn(iYear,om4,par)
#   om4=fwd(om4,fbar=f[,iYear]*1.2,sr=eq)
#   }
# 
# plot(FLStocks("fwd"=om,"0.8"=om2,"1.0"=om3,"1.2"=om4))

@@

# Simulation results

@@

@@

@@

@@

>>>>

<!-- =============================================================================================================== -->
<!-- ## Mackerel report                                                                                              -->
<!-- =============================================================================================================== -->

@@

<!-- =============================================================================================================== -->
<!-- Section 1: introduction                                                                                         -->
<!-- =============================================================================================================== -->

@@

This report deals with the evaluation of density dependent processes for `r mystkname` using Management Strategy Evaluation (MSE). Steps in the analysis:

1. Conditioning and summaries based on the 2022 ICES assessment (section 2)
2. Estimating Density Dependent effects based on equilibrium analyses and explore DD before setting up the OMs (section 3)
3. Setting up the Operating Models (OM) (section 4)
4. Running MSE's (section 5)

Four alternatives OMs have been included in the analyses:

@@

All MSE's have been developed within the FLR framework (https://flr-project.org/) and all the code is stored on github (https://github.com/martinpastoors/ddmse).

All data and results are available on DropBox (https://www.dropbox.com/sh/k87x074xqw7sgae/AAAmF980iR2n24wTkqhOhnpfa?dl=0)

<!-- =============================================================================================================== -->
<!-- Section 2: conditioning and summaries of ICES assessment                                                        -->
<!-- =============================================================================================================== -->

# Conditioning and summaries based on the 2022 ICES assessment

<!-- =============================================================================================================== -->
<!-- Section 3: Estimating Density Dependent effects based on equilibrium analyses                                   -->
<!-- =============================================================================================================== -->

# Estimating Density Dependent effects based on equilibrium analyses

@@

knitr::include_graphics(path=file.path(resultsdir, paste0(mystk,"_eq_yield.jpg")))

@@

<!-- =============================================================================================================== -->
<!-- Section 4: Setting up the Operating Models (OM)                                                                 -->
<!-- =============================================================================================================== -->

# Setting up the Operating Models (OM)

@@

@@

<!-- =============================================================================================================== -->
<!-- Section 5: Running MSE's                                                                                        -->
<!-- =============================================================================================================== -->

# Running MSE's

<!-- =============================================================================================================== -->
<!-- Section 6: Discussion and conclusions                                                                           -->
<!-- =============================================================================================================== -->

@@

<!-- =============================================================================================================== -->
<!-- Funding                                                                                                         -->
<!-- =============================================================================================================== -->

@@

<!-- =============================================================================================================== -->
<!-- References                                                                                                      -->
<!-- =============================================================================================================== -->

@@

<!-- =============================================================================================================== -->
<!-- Annex 1: OM conditioning                                                                           -->
<!-- =============================================================================================================== -->

@@

<!-- =============================================================================================================== -->
<!-- Annex 2: Density dependent processes                                                                           -->
<!-- =============================================================================================================== -->
